No meaningful effects of COVID-19 related social media use on well-being

### 2023-01-30 manuscript.Rmd
- Changed URLs

The hypotheses, the sample, the measures, the analyses, and the inference criteria (SESOI, _p_-value) were preregistered on the Open Science Framework, accessible here: https://osf.io/87b24/?view_only=b2289b6fec214fa88ee75a18d45c18f3.
Because in this study I analyze data from an already existing large-scale data set, the preregistration was done prior to accessing the data.
The preregistration was designed on the basis of the panel documentation online [@kittelAustrianCoronaPanel2020].
In some cases, it was impossible to execute the analyses as I had originally planned, for example because some properties of the variables only became apparent when seeing the actual data.
The most relevant deviations are reported below, and a complete list of all changes can be found in the online [companion website](https://XMtRA.github.io/Austrian_Corona_Panel_Project) (https://XMtRA.github.io/Austrian_Corona_Panel_Project).

@@

To find out whether the inferences were robust across plausible but subordinate analyses, I conducted additional exploratory analyses. 
I reran the analyses (a) with additional not-preregistered covariates such as trust in media or government, (b) without covariates, (c) with single imputation, and (d) without imputation.
For more information on the analyses, a complete documentation of the models and results, and all additional analyses, see [companion website](https://XMtRA.github.io/Austrian_Corona_Panel_Project).
<!-- The additional analyses are reported on the [companion website](https://XMtRA.github.io/Austrian_Corona_Panel_Project/analyses_additional.html). -->
<!-- For example, all within-person standardized COVID-19 related types of social media use or channels were significantly smaller than $\beta$ = |.05|, again supporting that effects were negligible. -->

@@

All the stimuli, presentation materials, analysis scripts, and a reproducible version of the manuscript can be found on the companion website (https://XMtRA.github.io/Austrian_Corona_Panel_Project).

>>>>

The hypotheses, the sample, the measures, the analyses, and the inference criteria (SESOI, _p_-value) were preregistered on the Open Science Framework, accessible here: https://osf.io/87b24/?view_only=b2289b6fec214fa88ee75a18d45c18f3.
Because in this study I analyze data from an already existing large-scale data set, the preregistration was done prior to accessing the data.
The preregistration was designed on the basis of the panel documentation online [@kittelAustrianCoronaPanel2020].
In some cases, it was impossible to execute the analyses as I had originally planned, for example because some properties of the variables only became apparent when seeing the actual data.
The most relevant deviations are reported below, and a complete list of all changes can be found in the online [companion website](https://tdienlin.github.io/Austrian_Corona_Panel) (https://tdienlin.github.io/Austrian_Corona_Panel).

@@

To find out whether the inferences were robust across plausible but subordinate analyses, I conducted additional exploratory analyses. 
I reran the analyses (a) with additional not-preregistered covariates such as trust in media or government, (b) without covariates, (c) with single imputation, and (d) without imputation.
For more information on the analyses, a complete documentation of the models and results, and all additional analyses, see [companion website](https://tdienlin.github.io/Austrian_Corona_Panel).
<!-- For example, all within-person standardized COVID-19 related types of social media use or channels were significantly smaller than $\beta$ = |.05|, again supporting that effects were negligible. -->

@@

All the stimuli, presentation materials, analysis scripts, and a reproducible version of the manuscript can be found on the companion website (https://tdienlin.github.io/Austrian_Corona_Panel).

### 2023-01-30 manuscript.tex
- Changed URLs

The hypotheses, the sample, the measures, the analyses, and the inference criteria (SESOI, \emph{p}-value) were preregistered on the Open Science Framework, accessible here: \url{https://osf.io/87b24/?view_only=b2289b6fec214fa88ee75a18d45c18f3}.
Because in this study I analyze data from an already existing large-scale data set, the preregistration was done prior to accessing the data.
The preregistration was designed on the basis of the panel documentation online (Kittel et al., 2020).
In some cases, it was impossible to execute the analyses as I had originally planned, for example because some properties of the variables only became apparent when seeing the actual data.
The most relevant deviations are reported below, and a complete list of all changes can be found in the online \href{https://XMtRA.github.io/Austrian_Corona_Panel_Project}{companion website} (\url{https://XMtRA.github.io/Austrian_Corona_Panel_Project}).

@@

To find out whether the inferences were robust across plausible but subordinate analyses, I conducted additional exploratory analyses.
I reran the analyses (a) with additional not-preregistered covariates such as trust in media or government, (b) without covariates, (c) with single imputation, and (d) without imputation.
For more information on the analyses, a complete documentation of the models and results, and all additional analyses, see \href{https://XMtRA.github.io/Austrian_Corona_Panel_Project}{companion website}.

@@

All the stimuli, presentation materials, analysis scripts, and a reproducible version of the manuscript can be found on the companion website (\url{https://XMtRA.github.io/Austrian_Corona_Panel_Project}).

>>>>

The hypotheses, the sample, the measures, the analyses, and the inference criteria (SESOI, \emph{p}-value) were preregistered on the Open Science Framework, accessible here: \url{https://osf.io/87b24/?view_only=b2289b6fec214fa88ee75a18d45c18f3}.
Because in this study I analyze data from an already existing large-scale data set, the preregistration was done prior to accessing the data.
The preregistration was designed on the basis of the panel documentation online (Kittel et al., 2020).
In some cases, it was impossible to execute the analyses as I had originally planned, for example because some properties of the variables only became apparent when seeing the actual data.
The most relevant deviations are reported below, and a complete list of all changes can be found in the online \href{https://tdienlin.github.io/Austrian_Corona_Panel}{companion website} (\url{https://tdienlin.github.io/Austrian_Corona_Panel}).

@@

To find out whether the inferences were robust across plausible but subordinate analyses, I conducted additional exploratory analyses.
I reran the analyses (a) with additional not-preregistered covariates such as trust in media or government, (b) without covariates, (c) with single imputation, and (d) without imputation.
For more information on the analyses, a complete documentation of the models and results, and all additional analyses, see \href{https://tdienlin.github.io/Austrian_Corona_Panel}{companion website}.

@@

All the stimuli, presentation materials, analysis scripts, and a reproducible version of the manuscript can be found on the companion website (\url{https://tdienlin.github.io/Austrian_Corona_Panel}).
